Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-13 MDPI_submission.Rmd
Commit 2023-12-13 14:14

setorder(TSI, -slope.stat_sig)
rownames(TSI) <- NULL
names(TSI) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
TSIslopeAll <- TSI[`Sky condition` == "All sky cond."]
```

@@

# 
# names(LT)    <- c("Trend [%/year]",
#                   "Trend p-value",
#                   "Sky conditions",
#                   "Days with data",
#                   "Statistical signif. [%]")

## no need all are 100%

@@

## order columns
LT1 <- LT[,c(
      "Sky conditions",
      "Trend [%/year]",
      "Trend p-value",
      "Pearson cor.",
      "Days"
      )]

>>>>

# setorder(TSI, -slope.stat_sig)
# rownames(TSI) <- NULL
# names(TSI) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
# 
# TSIslopeAll <- TSI[`Sky condition` == "All sky cond."]
TSIslopeAll <- TSI[DATA == "All sky cond."]
```

@@

LT$slope.stat_sig  <- NULL
LT$`Trend p-value` <- NULL
LT$N_eff           <- NULL

@@

## order columns
# LT1 <- LT[,c(
#       "Sky conditions",
#       "Trend [%/year]",
#       "Trend p-value",
#       "Pearson cor.",
#       "Days"
#       )]
LT1 <- LT

### 2023-12-13 MDPI_submission.tex
Commit 2023-12-13 14:14

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
Sky conditions & Trend [\%/year] & Trend p-value & Pearson cor. & Days\\
\midrule
All skies & 0.377 & 0 & 0.0913 & 10251\\
Clear skies & 0.097 & 0 & 0.1381 & 2689\\
Cloudy skies & 0.408 & 0 & 0.0810 & 4937\\
\bottomrule
\end{tabu}
\end{table}

>>>>

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X}
\toprule
Trend [\%/year] & Rsqrd & Pearson cor. & Sky conditions & Days & t\_eff & t\_eff\_cri & conf\_2.5 & conf\_97.5 & mean\_clima & ChangeWpY\\
\midrule
0.376 & 0.00830 & 0.0911 & All skies & 10250 & 4.727 & 1.96 & 0.000811 & 0.001246 & 387 & 1.45\\
0.097 & 0.01908 & 0.1381 & Clear skies & 2689 & 0.476 & 1.96 & 0.000194 & 0.000338 & 515 & 0.50\\
0.408 & 0.00657 & 0.0810 & Cloudy skies & 4937 & 3.566 & 1.96 & 0.000733 & 0.001499 & 290 & 1.18\\
\bottomrule
\end{tabu}
\end{table}
